---
title: "Electricity Bills Analysis - ENCEVI 2018"
author: "[Mauricio Hernandez](http://mauricioh2.com)"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    code_folding: hide
    self_contained: true
    thumbnails: true
    lightbox: false
    highlight: tango
---

```{r}
#Remove all objects from current workspace and call garbage collector
rm(list=ls())
gc()
```

```{r sh, echo=TRUE, eval=TRUE, warning = FALSE, message = FALSE}
UsePackage <- function(p) {
  # Installs the package if it hasn't already been installed.
  # Includes the library into the session, if the package has been installed.
  #
  # Args:
  #   p: package name
  #   installed.packages(): The other vector. x and y must have the same length, greater 
  #                         than one, with no missing values.
  # 
  # Returns:
  #   N/A
  if (!is.element(p, installed.packages()[,1])){
    install.packages(p, dep = TRUE)
  }
  require(p, character.only = TRUE)
}
```

```{r knitr_init, echo=FALSE, results="asis", cache=FALSE, warning = FALSE}
#options(max.print = "75")
UsePackage("knitr")
opts_chunk$set(echo = FALSE,
	             cache = FALSE,
               prompt = FALSE,
               tidy = FALSE,
               comment = NA,
               message = FALSE,
               warning = FALSE
               )
opts_knit$set(width = 100,
           plain.ascii = FALSE,       # This is very handy in all Rmd documents
           style = "rmarkdown",        # This too
           footnote = NA,             # Avoids footnotes which would clutter the results
           subtitle.emphasis = FALSE)  # This is a setting to experiment with - according to)

```

```{r, echo=TRUE, eval=TRUE, warning = FALSE, message = FALSE}
#devtools::install_github("ropensci/plotly")
```

```{r, echo=TRUE, eval=TRUE, warning = FALSE, message = FALSE}
Sys.setenv("plotly_username" = "mauricioh2")
Sys.setenv("plotly_api_key" = "CzXpBQKn6zRQj1ExEd5O")
```

```{r load_packages, echo=TRUE, eval=TRUE, warning = FALSE, message = FALSE}
##Load and attach add-on packages
UsePackage('ProjectTemplate')
UsePackage('stringr')
UsePackage('psych')
UsePackage('ggplot2')
UsePackage('dplyr') 
UsePackage('reshape2')
UsePackage('plotly')
UsePackage('processx')
UsePackage('doBy')
UsePackage('foreign')   
UsePackage('survey')
UsePackage('reticulate') 
UsePackage('tidyverse')
UsePackage('broman') #https://kbroman.org/knitr_knutshell/pages/Rmarkdown.html
UsePackage("rmdformats")
UsePackage('remotes')
UsePackage('summarytools')
```
```{r, echo=TRUE, eval=TRUE, warning = FALSE, message = FALSE}
st_css()
```
##Loading datasets
```{r, echo=TRUE, eval=TRUE, warning = FALSE, message = FALSE}
#This table contains characteristics on the main final uses of energy in the 
#dwellings according to the socioeconomic characteristics of the households
df.encevi <- read.csv("input/encevi.csv")

#This table contains the characteristics of the dwellings inhabited by the
#members of the households surveyed.
df.dwelling <- read.csv("input/vivienda.csv")

#In this table are contained the characteristics of the households that 
#inhabit the dwellings.
df.household <- read.csv("input/hogar.csv")

#importing data of summer months per region
df.summer.months <- read.csv("input/summer_by_state_cfe_052419.csv")
```

```{r, echo=TRUE, eval=TRUE, warning = FALSE, message = FALSE}
# Get municipality codes ordered and cleaned, results are stored in 
# folder "/input", as INEGI_agem_short.csv, these data was provided 
# by INEGI and it is related to ENCEVI 2018 survey
#source('municipality_codes_inegi.R')

# Get tariffs and municipality codes by household ids, the results are 
# stored in folder "/input", as agem_tariff_byfolio.csv. 
source("merge_ids_agem_tariffs.R")
df.tariffs<- read.csv("input/agem_tariff_byfolio.csv")
```

## Cleaning and merging dataframes
```{r, echo=TRUE, eval=TRUE, warning = FALSE, message = FALSE}
names(df.encevi) <- tolower(colnames(df.encevi))
names(df.dwelling) <- tolower(colnames(df.dwelling)) 
names(df.household) <- tolower(colnames(df.household)) 

#Rename first column as folio. This piece of code corrects a bug in the command
colnames(df.encevi)[1] <- "folio"
colnames(df.dwelling)[1] <- "folio"
colnames(df.household)[1] <- "folio"
colnames(df.dwelling)[colnames(df.dwelling)=="entidad"] <- "state.id"
```

```{r, echo=TRUE, eval=TRUE, warning = FALSE, message = FALSE}
# Merging ENCEVI and Dwelling datasets
df.enc.dwell <- merge(df.encevi, df.dwelling, by="folio")

# Merging encevi-dwelling dataframe with INEGI municipality codes dataframe
df.enc.dwell <- merge(df.enc.dwell, df.tariffs, by="folio")
```

Storing results of tariffs per 
```{r}
#write.csv(df.enc.dwell, "./output/encevi_dwelling.csv", row.names=TRUE, na="")
#show table of tariffs with missing values
table(df.enc.dwell$tariff, exclude = NULL)
prop.table(table(df.enc.dwell$tariff, exclude = NULL))
```


```{r, echo=TRUE, eval=TRUE, warning = FALSE, message = FALSE}
df.enc.dwell$region.f <- factor(df.enc.dwell$region,
                                levels = c(1, 2, 3),
                                labels = c("Extreme hot", "Temperate", "Tropical"))

df.enc.dwell$tipo_tarif.f <- factor(df.enc.dwell$tipo_tarif,
                               levels = c(0, 1, 2, 3, 4, 5, 6, 7, 8, 9),
                               labels = c("2", "1", "1A", "1B", "1C", "1D", 
                                          "1E", "1F", "DAC", "Don't know"))

df.enc.dwell$state.f <- factor(df.enc.dwell$state.id,
                               levels = c("1", "2", "3", "4", "5", "6", "7", 
                                          "8", "9", "10","11", "12", "13", "14", 
                                          "15", "16", "17", "18", "19", "20", 
                                          "21", "22", "23", "24", "25", "26", 
                                          "27", "28", "29", "30", "31", "32"),
                               labels = c("Aguascalientes", "Baja California", 
                                          "Baja California Sur", "Campeche", 
                                          "Coahuila", "Colima", "Chiapas", 
                                          "Chihuahua", "Mexico City", 
                                          "Durango", "Guanajuato", "Guerrero", 
                                          "Hidalgo", "Jalisco", "Mexico", 
                                          "Michoacan", "Morelos", "Nayarit", 
                                          "NuevoLeon", "Oaxaca", "Puebla", 
                                          "Queretaro", "Quintana Roo", 
                                          "San Luis Potosi", "Sinaloa", 
                                          "Sonora", "Tabasco", "Tamaulipas", 
                                          "Tlaxcala", "Veracruz", "Yucatan", 
                                          "Zacatecas"))
```

```{r, echo=TRUE, eval=TRUE, warning = FALSE, message = FALSE}
df.summer.months <- subset(df.summer.months, year==2017, 
                        select=c('state.id', 'month', 'summer'))
#df.enc.dwell <- merge(df.enc.dwell, df.summer.months, by="state.id")
```

##Dwellings Connected to the Grid by Region
```{r, echo=TRUE, eval=TRUE, warning = FALSE, message = FALSE}
# Survey design construction (mmc), this computes the statistical errors
mmc <- svydesign(id=~upm, strata=~est_dis, 
                 data=df.enc.dwell, weights=~ factor_sem)

df.enc.dwell$dummy.house <- 1
# Estimación total de viviendas particulares habitadas 
tb.dwell <- svytotal(df.enc.dwell$dummy.house, mmc)

total.dwell <- sum(df.enc.dwell$factor_sem)
sum(df.enc.dwell$dummy.house)
total.dwell
```
Number of dwellings surveyed and number of dwellings represented: `r sum(df.enc.dwell$dummy.house)` and `r total.dwell`

*Dwellings Connected to the Grid by Region
```{r, echo=TRUE, eval=TRUE, warning = FALSE, message = FALSE}
#Get dwellings connected to the grid
df.enc.dwell$grid <- ifelse(df.enc.dwell$electri %in% "1", 1 ,0) 
#Total dwellings with insulation
total.dwell.grid <- sum(df.enc.dwell$grid * df.enc.dwell$factor_sem)

table(df.enc.dwell$grid)
total.dwell.grid
```
Number of dwellings connected to the grid `r myround(total.dwell.grid, 2)`


```{r results="asis"}
freq(df.enc.dwell$grid, weight = df.enc.dwell$factor_sem, report.nas = FALSE, plain.ascii = FALSE, style = "simple", method = "render", headings = FALSE)
```

Number of dwellings by region
```{r, echo=TRUE, eval=TRUE, warning = FALSE, message = FALSE}
# Estimación por Región del total de viviendas particulares habitadas 
#tb.dwell.region <- svyby(~dummy.house, by=~region.f, mmc, svytotal)  

##Pr01 <- svyby(~a01, by=~REGION, MMC, svytotal)  
#ea01n <- tb.dwell[[1]]  # Estimación puntual 
#er01n <- t(tb.dwell.region[2]) # Estimación puntual-Región 
#ea01e <- SE(tb.dwell)   # Error estándar 
#er01e <- t(data.frame(SE(tb.dwell.region)))  # Error estándar-Región 

#tb.dwell
#tb.dwell.region
```

Number of dwellings connected to the grid by region
```{r, echo=TRUE, eval=TRUE, warning = FALSE, message = FALSE}
# Survey design construction, this computes the statistical errors
# Construye el Diseño de la Encuesta (mmc) para calcular las Precisiones Estadísticas 
#mmc <- svydesign(id=~upm, strata=~est_dis, data=df.enc.dwell, weights=~ factor_sem)

## Estimación total de viviendas particulares habitadas 
#tb.dwell <- svytotal(df.enc.dwell$dummy.house, mmc)

#tb.grid.region <- svyby(~dummy.house, by=~region.f+grid, mmc, svytotal) 
#colnames(tb.grid.region)[colnames(tb.grid.region)=="dummy.house"] <-"dwellings"

#tb.grid.region <- merge(tb.grid.region, tb.dwell.region[,c("region.f","dummy.house")], by="region.f")
#colnames(tb.grid.region)[colnames(tb.grid.region)=="dummy.house"] <- "dwellings.region"

#tb.grid.region <- transform(tb.grid.region, percent.grid = tb.grid.region$dwellings / #tb.grid.region$dwellings.region)
#tb.grid.region
```

```{r}
table(df.enc.dwell$grid)
## Eliminate records of dwellings that are not connected to the grid
df.enc.dwell <- subset(df.enc.dwell, grid==1)
```

##Electricity bill dates
```{r, echo=TRUE, eval=TRUE, warning = FALSE, message = FALSE}
df.enc.dwell$inicia1[df.enc.dwell$inicia1 == 99] <-  NA 
df.enc.dwell$mes_inic1[df.enc.dwell$mes_inic1 == 99] <-  NA
df.enc.dwell$inicia2[df.enc.dwell$inicia2 == 99] <-  NA
df.enc.dwell$mes_inic2[df.enc.dwell$mes_inic2 == 99] <-  NA
df.enc.dwell$final1[df.enc.dwell$final1 == 99] <-  NA 
df.enc.dwell$mes_final1[df.enc.dwell$mes_final1 == 99] <-  NA
df.enc.dwell$final2[df.enc.dwell$final2 == 99] <- NA
df.enc.dwell$mes_final2[df.enc.dwell$mes_final2 == 99]  <-  NA

df.enc.dwell$cons_med1[df.enc.dwell$cons_med1 >= 98888 ] <- NA
df.enc.dwell$cons_med2[df.enc.dwell$cons_med2 >= 98888 ] <- NA

#df.enc.dwell$inicia1 <- as.integer(df.enc.dwell$inicia1)
```


Calculating days of consumption for first electricity bill
```{r, echo=FALSE, eval=TRUE, warning = FALSE, message = FALSE, results = FALSE}
df.enc.dwell$bill.ini.date1 <- NA
df.enc.dwell$bill.end.date1 <- NA

# The data was obtained from January 2018 to June 2018.
# So the bills could be from 2017 or 2018.
# As the survey does not report the year of the electricity bill, it is calculated here
df.enc.dwell$year_ini1 <- "2018"
df.enc.dwell$year_end1 <- "2018"

# Case 1. If the initial period of the bill is from june to december, 
# it is assumed that the year of the initial period is 2017
df.enc.dwell$year_ini1[df.enc.dwell$mes_inic1 >= 6] <- 2017

# Case 2. If the final period of the bill is from july to december, 
# it is assumed that the year of the final period is 2017
df.enc.dwell$year_end1[df.enc.dwell$mes_final1 >= 7] <- 2017

# Case 3. If the initia month period of the bill is higher than the final month, 
# it is assumed that the year of the initial period is 2017
df.enc.dwell$year_ini1[df.enc.dwell$mes_inic1 > df.enc.dwell$mes_final1] <- 2017

df.enc.dwell$bill.ini.date1 <-  str_replace_all(paste(df.enc.dwell$mes_inic1, "-" , 
                                                         df.enc.dwell$inicia1, "-", 
                                                         df.enc.dwell$year_ini1),
                                                   pattern=" ", repl="")

df.enc.dwell$bill.end.date1 <-  str_replace_all(paste(df.enc.dwell$mes_final1, "-" , 
                                                         df.enc.dwell$final1, "-", 
                                                         df.enc.dwell$year_end1),
                                                   pattern=" ", repl="")

df.enc.dwell$bill.ini.date1 <- as.Date(as.character(df.enc.dwell$bill.ini.date1), 
                                          format="%m-%d-%Y")
df.enc.dwell$bill.end.date1 <- as.Date(as.character(df.enc.dwell$bill.end.date1), 
                                          format="%m-%d-%Y")
df.enc.dwell$bill.days1 <- as.integer((df.enc.dwell$bill.end.date1 - df.enc.dwell$bill.ini.date1))


# After obtaining the number of days of the period in the electricity bill. 
# There are still some special cases that are corrected here.
# Case 4. If the period in the electricity bill is longer than 1 year, the initial year is assumed to be 2018
df.enc.dwell$year_ini1[df.enc.dwell$bill.days1 >= 365 & 
                            (df.enc.dwell$mes_inic1 <= df.enc.dwell$mes_final1)] <- 2018

# Case 5. If the period in the electricity bill is negative, the initial year is assumed to be 2017
df.enc.dwell$year_ini1[df.enc.dwell$bill.days1 < 0] <- 2017

df.enc.dwell$bill.end.date1 <-  str_replace_all(paste(df.enc.dwell$mes_final1, "-" , 
                                                         df.enc.dwell$final1, "-", df.enc.dwell$year_end1),
                                                   pattern=" ", repl="")

df.enc.dwell$bill.ini.date1 <-  str_replace_all(paste(df.enc.dwell$mes_inic1, "-" , 
                                                         df.enc.dwell$inicia1, "-", df.enc.dwell$year_ini1),
                                                   pattern=" ", repl="")

df.enc.dwell$bill.end.date1 <-  str_replace_all(paste(df.enc.dwell$mes_final1, "-" , 
                                                         df.enc.dwell$final1, "-", df.enc.dwell$year_end1),
                                                   pattern=" ", repl="")

df.enc.dwell$bill.ini.date1 <- as.Date(as.character(df.enc.dwell$bill.ini.date1), format="%m-%d-%Y")
df.enc.dwell$bill.end.date1 <- as.Date(as.character(df.enc.dwell$bill.end.date1), format="%m-%d-%Y")
df.enc.dwell$bill.days1 <- as.integer((df.enc.dwell$bill.end.date1 - df.enc.dwell$bill.ini.date1))

df.enc.dwell$bill.days1[df.enc.dwell$bill.days1 < 0 ] <- NA
df.enc.dwell$bill.days1[df.enc.dwell$bill.days1 > 180 ] <- NA
```


Calculating days of consumption for second electricity bill
```{r, echo=FALSE, eval=TRUE, warning = FALSE, message = FALSE, results = FALSE}
df.enc.dwell$bill.ini.date2 <- NA
df.enc.dwell$bill.end.date2 <- NA

# The data was obtained from January 2018 to June 2018.
# So the bills could be from 2017 or 2018.
# As the survey does not report the year of the electricity bill, it is calculated here
df.enc.dwell$year_ini2 <- "2018"
df.enc.dwell$year_end2 <- "2018"

# Case 1. If the initial period of the bill is from june to december, 
# it is assumed that the year of the initial period is 2017
df.enc.dwell$year_ini2[df.enc.dwell$mes_inic2 >= 6] <- 2017

# Case 2. If the final period of the bill is from july to december, 
# it is assumed that the year of the final period is 2017
df.enc.dwell$year_end2[df.enc.dwell$mes_final2 >= 7] <- 2017

# Case 3. If the initia month period of the bill is higher than the final month, 
# it is assumed that the year of the initial period is 2017
df.enc.dwell$year_ini2[df.enc.dwell$mes_inic2 > df.enc.dwell$mes_final2] <- 2017

df.enc.dwell$bill.ini.date2 <-  str_replace_all(paste(df.enc.dwell$mes_inic2, "-" , 
                                                         df.enc.dwell$inicia1, "-", 
                                                         df.enc.dwell$year_ini2),
                                                   pattern=" ", repl="")

df.enc.dwell$bill.end.date2 <-  str_replace_all(paste(df.enc.dwell$mes_final2, "-" , 
                                                         df.enc.dwell$final1, "-", 
                                                         df.enc.dwell$year_end2),
                                                   pattern=" ", repl="")

df.enc.dwell$bill.ini.date2 <- as.Date(as.character(df.enc.dwell$bill.ini.date2), 
                                          format="%m-%d-%Y")
df.enc.dwell$bill.end.date2 <- as.Date(as.character(df.enc.dwell$bill.end.date2), 
                                          format="%m-%d-%Y")
df.enc.dwell$bill.days2 <- as.integer((df.enc.dwell$bill.end.date2 - df.enc.dwell$bill.ini.date2))


# After obtaining the number of days of the period in the electricity bill. 
# There are still some special cases that are corrected here.
# Case 4. If the period in the electricity bill is longer than 1 year, the initial year is assumed to be 2018
df.enc.dwell$year_ini2[df.enc.dwell$bill.days2 >= 365 & 
                            (df.enc.dwell$mes_inic2 <= df.enc.dwell$mes_final2)] <- 2018

# Case 5. If the period in the electricity bill is negative, the initial year is assumed to be 2017
df.enc.dwell$year_ini2[df.enc.dwell$bill.days2 < 0] <- 2017

df.enc.dwell$bill.end.date2 <-  str_replace_all(paste(df.enc.dwell$mes_final2, "-" , 
                                                         df.enc.dwell$final1, "-", df.enc.dwell$year_end2),
                                                   pattern=" ", repl="")

df.enc.dwell$bill.ini.date2 <-  str_replace_all(paste(df.enc.dwell$mes_inic2, "-" , 
                                                         df.enc.dwell$inicia1, "-", df.enc.dwell$year_ini2),
                                                   pattern=" ", repl="")

df.enc.dwell$bill.end.date2 <-  str_replace_all(paste(df.enc.dwell$mes_final2, "-" , 
                                                         df.enc.dwell$final1, "-", df.enc.dwell$year_end2),
                                                   pattern=" ", repl="")

df.enc.dwell$bill.ini.date2 <- as.Date(as.character(df.enc.dwell$bill.ini.date2), format="%m-%d-%Y")
df.enc.dwell$bill.end.date2 <- as.Date(as.character(df.enc.dwell$bill.end.date2), format="%m-%d-%Y")
df.enc.dwell$bill.days2 <- as.integer((df.enc.dwell$bill.end.date2 - df.enc.dwell$bill.ini.date2))

df.enc.dwell$bill.days2[df.enc.dwell$bill.days2 < 0 ] <- NA
df.enc.dwell$bill.days2[df.enc.dwell$bill.days2 > 180 ] <- NA
```

```{r, echo=TRUE, eval=TRUE, warning = FALSE, message = FALSE}
describe(df.enc.dwell$bill.days1)
describe(df.enc.dwell$bill.days2)
```

```{r, echo=TRUE, eval=TRUE, warning = FALSE, message = FALSE}
attach(df.enc.dwell)
#df.bill.test <- subset(df.enc.dwell, bill.days1 >= 25, 
#                        select=c('bill.days1', 'mes_inic1', 'final1', 'mes_final1', 
#                                 'inicia1', 'bill.ini.date1', 'bill.end.date1', 'cons_med1')) 

df.bill.test2 <- subset(df.enc.dwell, bill.days2 >= 0, 
                        select=c('bill.days1', 'bill.days2', 'bill.ini.date1', 
                                 'bill.ini.date2', 'bill.end.date1',
                                 'bill.end.date2', 'cons_med1', 'cons_med2', 
                                 'cond_energ', 'local_com', 'elect_loc'))
detach(df.enc.dwell)
#sort(df.bill.error$bill.days1,decreasing=FALSE)
df.bill.test2[order(-df.bill.test2$bill.days2),]
```

Reference: https://cran.r-project.org/web/packages/summarytools/vignettes/Introduction.html

```{r, echo=FALSE, eval=TRUE, warning = FALSE, message = FALSE, results = FALSE}
attach(df.enc.dwell)
df.bill.error <- subset(df.enc.dwell, bill.days1 < 91, 
                        select=c('bill.days1', 'mes_inic1', 'final1', 'mes_final1', 
                                 'inicia1', 'bill.ini.date1', 'bill.end.date1', 'cons_med1'))
detach(df.enc.dwell)
#sort(df.bill.error$bill.days1,decreasing=FALSE)
df.bill.error[order(df.bill.error$bill.days1),]
```
```{r, echo=FALSE, eval=TRUE, warning = FALSE, message = FALSE, results = FALSE}
attach(df.enc.dwell)
#df.bill.test <- subset(df.enc.dwell, bill.days1 >= 25, 
#                        select=c('bill.days1', 'mes_inic1', 'final1', 'mes_final1', 
#                                 'inicia1', 'bill.ini.date1', 'bill.end.date1', 'cons_med1')) 

df.bill.test <- subset(df.enc.dwell, bill.days1 >= 25 & local_com == 2, 
                        select=c('bill.days1', 'bill.ini.date1', 'bill.end.date1', 
                                 'cons_med1', 'cond_energ', 'local_com', 'elect_loc', 'cons_med2'))

detach(df.enc.dwell)
#sort(df.bill.error$bill.days1,decreasing=FALSE)
#df.bill.test$cons.day <-  df.bill.test /
df.bill.test <- transform(df.bill.test, bill.cons.day = df.bill.test$cons_med1 / df.bill.test$bill.days1)

df.bill.test[order(df.bill.test$bill.cons.day),]


describe(df.bill.test$bill.cons.day)
```


# Tariffs
Reference: http://www.cfe.mx/tarifas/Pages/Tarifas.aspx
```{r, echo=FALSE, eval=TRUE, warning = FALSE, message = FALSE, results = FALSE}
#summary(df.enc.dwell$tariff)
#df.enc.dwell$tariff(is.na(df.enc.dwell$tariff)) <- "Don't know"
df.enc.dwell$tariff <- as.character(df.enc.dwell$tariff)
df.enc.dwell$tipo_tarif.f <- as.character(df.enc.dwell$tipo_tarif.f)

df.enc.dwell$tariff[df.enc.dwell$tariff==""] <- "Don't know"

df.enc.dwell$tariff.m <- recode(df.enc.dwell$tipo_tarif.f, "Don't know"= df.enc.dwell$tariff)
#df.enc.dwell$tariff.m <- df.enc.dwell$tariff.m %>% replace_na("Don't know")

df.enc.dwell$tipo_tarif.f <- factor(df.enc.dwell$tipo_tarif,
                               levels = c(0, 1, 2, 3, 4, 5, 6, 7, 8, 9),
                               labels = c("2", "1", "1A", "1B", "1C", "1D", 
                                          "1E", "1F", "DAC", "Don't know"))
df.enc.dwell$tariff.m <- as.factor(df.enc.dwell$tariff.m)
df.enc.dwell$tariff.m <- factor(df.enc.dwell$tariff.m,
                               levels = c("2", "1", "1A", "1B", "1C", "1D", 
                                          "1E", "1F", "DAC", "Don't know"),
                               labels = c("2", "1", "1A", "1B", "1C", "1D", 
                                          "1E", "1F", "DAC", "Don't know"))
prop.table(table(df.enc.dwell$tipo_tarif.f, exclude = NULL))*100
prop.table(table(df.enc.dwell$tariff.m, exclude = NULL))*100
```


```{r, echo=TRUE, eval=TRUE, warning = FALSE, message = FALSE}
table(df.enc.dwell$state.f, df.enc.dwell$tariff.m, exclude = NULL)
```

```{r, echo=TRUE, eval=TRUE, warning = FALSE, message = FALSE}
table(df.enc.dwell$state.f, df.enc.dwell$tipo_tarif.f, exclude = NULL)
```
